Bioverse: Origins of Life

### 2023-12-15 src/tex/glossary.tex
include variables, new gls entries
add short results, discussion, conclusion on spT dependency
fix compilation errors

\newglossaryentry{HST}{name={HST}, description={Hubble Space Telescope}, first={Hubble Space Telescope (HST)}}
\newglossaryentry{NIR}{name={NIR}, description={Near-Infrared}, first={near-infrared (NIR)}}
\newglossaryentry{MIR}{name={MIR}, description={Mid-Infrared}, first={mid-infrared (MIR)}}
\newglossaryentry{FIR}{name={FIR}, description={Far-Infrared}, first={far-infrared (FIR)}}
\newglossaryentry{FUV}{name={FUV}, description={Far-Ultraviolet}, first={far-Ultraviolet (FUV)}}
\newglossaryentry{NUV}{name={NUV}, description={Near-Ultraviolet}, first={near-Ultraviolet (NUV)}}
\newglossaryentry{EUV}{name={EUV}, description={extreme-Ultraviolet}, first={extreme-Ultraviolet (EUV)}}
\newglossaryentry{SED}{name={SED}, description={Spectral energy distribution}, first={spectral energy distribution (SED)}, firstplural={spectral energy distributions (SEDs)}}
\newglossaryentry{ppm}{name={ppm}, description={parts per million}, first={parts per million (ppm)}}
\newglossaryentry{PDF}{name={PDF}, description={Probability density function}, first={probability density function (PDF)}, firstplural={probability density functions (PDF)}}
\newglossaryentry{PLATO}{name={PLATO}, description={PLAnetary Transits and Oscillations of stars}, first={PLATO~\citep[][]{Rauer2014}}}
\newglossaryentry{PSF}{name={PSF},description={Point Spread Function}, first={point spread function (PSF)}, firstplural={point spread functions (PSF)}}
\newglossaryentry{SFD}{name={SFD}, description={Size frequency distribution}, first={size frequency distribution (SFD)}, firstplural={Size frequency distributions (SFD)}}
\newglossaryentry{SNR}{name={SNR}, description={Signal-to-noise ratio}, first={signal-to-noise ratio (SNR)}}
\newglossaryentry{RV}{name={RV}, description={Radial Velocity}, first={Radial Velocity (RV)}, firstplural={Radial Velocities (RV)}}
\newglossaryentry{TTV}{name={TTV}, description={Transit Timing Variation}, first={transit timing variation (TTV)}, firstplural={transit timing variations (TTVs)}}
\newglossaryentry{TESS}{name={TESS}, description={Transiting Exoplanet Survey Satellite}, first={Transiting Exoplanet Survey Satellite~\citep[\textit{TESS},][]{Ricker2014}}}
\newglossaryentry{TIC}{name={TIC}, description={\textit{TESS} Input Catalog}, first={\textit{TESS} Input Catalog~\citep[TIC,][]{Stassun2018}}}
\newglossaryentry{JWST}{name={JWST}, description={James Webb Space Telescope}, first={James Webb Space Telescope~\citep[\textit{JWST},][]{Beichman2014}}}
\newglossaryentry{HZ}{name={HZ}, description={habitable zone}, first={habitable zone (HZ)}}
%\newglossaryentry{}{name={}, description={}, first={}, firstplural={}}

>>>>

\newglossaryentry{HST}{name={HST}, description={Hubble Space Telescope}, first={Hubble Space Telescope (HST)}}
\newglossaryentry{NIR}{name={NIR}, description={Near-Infrared}, first={near-infrared (NIR)}}
\newglossaryentry{MIR}{name={MIR}, description={Mid-Infrared}, first={mid-infrared (MIR)}}
\newglossaryentry{FIR}{name={FIR}, description={Far-Infrared}, first={far-infrared (FIR)}}
\newglossaryentry{FUV}{name={FUV}, description={Far-Ultraviolet}, first={far-Ultraviolet (FUV)}}
\newglossaryentry{NUV}{name={NUV}, description={Near-Ultraviolet}, first={near-Ultraviolet (NUV)}}
\newglossaryentry{EUV}{name={EUV}, description={extreme-Ultraviolet}, first={extreme-Ultraviolet (EUV)}}
\newglossaryentry{SED}{name={SED}, description={Spectral energy distribution}, first={spectral energy distribution (SED)}, firstplural={spectral energy distributions (SEDs)}}
\newglossaryentry{ppm}{name={ppm}, description={parts per million}, first={parts per million (ppm)}}
\newglossaryentry{PDF}{name={PDF}, description={Probability density function}, first={probability density function (PDF)}, firstplural={probability density functions (PDF)}}
\newglossaryentry{PLATO}{name={PLATO}, description={PLAnetary Transits and Oscillations of stars}, first={PLATO~\citep[][]{Rauer2014}}}
\newglossaryentry{PSF}{name={PSF},description={Point Spread Function}, first={point spread function (PSF)}, firstplural={point spread functions (PSF)}}
\newglossaryentry{SFD}{name={SFD}, description={Size frequency distribution}, first={size frequency distribution (SFD)}, firstplural={Size frequency distributions (SFD)}}
\newglossaryentry{SNR}{name={SNR}, description={Signal-to-noise ratio}, first={signal-to-noise ratio (SNR)}}
\newglossaryentry{RV}{name={RV}, description={Radial Velocity}, first={Radial Velocity (RV)}, firstplural={Radial Velocities (RV)}}
\newglossaryentry{TTV}{name={TTV}, description={Transit Timing Variation}, first={transit timing variation (TTV)}, firstplural={transit timing variations (TTVs)}}
\newglossaryentry{TESS}{name={TESS}, description={Transiting Exoplanet Survey Satellite}, first={Transiting Exoplanet Survey Satellite~\citep[\textit{TESS},][]{Ricker2014}}}
\newglossaryentry{TIC}{name={TIC}, description={\textit{TESS} Input Catalog}, first={\textit{TESS} Input Catalog~\citep[TIC,][]{Stassun2018}}}
\newglossaryentry{JWST}{name={JWST}, description={James Webb Space Telescope}, first={James Webb Space Telescope~\citep[\textit{JWST},][]{Beichman2014}}}
\newglossaryentry{HWO}{name={HWO}, description={Habitable Worlds Observatory}, first={Habitable Worlds Observatory (HWO)}}
\newglossaryentry{HZ}{name={HZ}, description={habitable zone}, first={habitable zone (HZ)}}
\newglossaryentry{EEC}{name={EEC}, description={exo-Earth candidate}, first={exo-Earth candidate (EEC)}, firstplural={exo-Earth candidates (EEC)}}
\newglossaryentry{ool}{name={OoL}, description={Origins of Life}, first={Origins of Life (OoL)}}
%\newglossaryentry{}{name={}, description={}, first={}, firstplural={}}

### 2023-12-15 src/tex/ms.tex
fix compilation errors

Let our observable be the inferred past \gls{NUV} flux of the planet $F_\mathrm{NUV}$.
Under Hypothesis $H_3$ (Equation \ref{eq:hypothesis-uv}), there exists a special unknown value of $F_\mathrm{NUV}$, noted $F_\mathrm{NUV, min}$ such that
\begin{array}{rcll}
P(L|\theta,H_3) & = & f_\mathrm{life} &\text{if } \theta>F_\mathrm{NUV, min}\\
P(L|\theta,H_3) & = & 0 &\text{otherwise}
\end{array}
where $f_\mathrm{life}$ is the unknown probability of abiogenesis.
The corresponding null hypothesis is that there exists no such special value of $F_\mathrm{NUV}$ and that
\begin{equation}
P(L|\theta,H_\mathrm{3, null}) = f_\mathrm{life}.
\end{equation}

@@

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo.pdf}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample with \gls{EEC} highlighted in green.
        Two of the three planet trajectories shown have extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections), our requirement for abiogenesis.}
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

Our main findings are:
\begin{enumerate}
    \item Models of the Origins of Life provide hypotheses that are testable with near-future exoplanet surveys.
    \item The required \gls{nuv} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{nuv} flux and current occurrence of biosignatures, both of which will soon be observationally accessible.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets, the distribution of host star spectral types in the sample, ...
        A direct imaging mission with the \gls{hwo} will require characterizing XXX planets ...
    \item Abiogenesis in the cyanosulfidic scenario strongly prefers late host star spectral types in a sample of transiting planets. Any potential biosignature detection on a planet around a star other than an M~dwarf would disvafor this scenario and any other \gls{ool} theory requiring extended periods of high \gls{nuv} irradiation.
\end{enumerate}

>>>>

Let our observable be the inferred past \gls{NUV} flux of the planet $F_\mathrm{NUV}$.
Under Hypothesis $H_3$ (Equation~\ref{eq:hypothesis-uv}), there exists a special unknown value of $F_\mathrm{NUV}$, noted $F_\mathrm{NUV, min}$ such that

\begin{align}
    P(L|\theta,H_3) & = & f_\mathrm{life} & \text{if } \theta>F_\mathrm{NUV, min}\\
    P(L|\theta,H_3) & = & 0 & \text{otherwise}
\end{align}

where $f_\mathrm{life}$ is the unknown probability of abiogenesis.
The corresponding null hypothesis is that there exists no such special value of $F_\mathrm{NUV}$ and that
\begin{equation}
P(L|\theta,H_\mathrm{3, null}) = f_\mathrm{life}.
\end{equation}

@@

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo.pdf}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample with \gls{EEC} highlighted in green.
        Two of the three planet trajectories shown have extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections), our requirement for abiogenesis.}
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

Our main findings are:
\begin{enumerate}
    \item Models of the Origins of Life provide hypotheses that are testable with near-future exoplanet surveys.
    \item The required \gls{NUV} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures, both of which will soon be observationally accessible.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets, the distribution of host star spectral types in the sample, ...
        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item Abiogenesis in the cyanosulfidic scenario strongly prefers late host star spectral types in a sample of transiting planets. Any potential biosignature detection on a planet around a star other than an M~dwarf would disvafor this scenario and any other \gls{ool} theory requiring extended periods of high \gls{NUV} irradiation.
\end{enumerate}
